Log or not - Analysis of ECDC forecasts

### 2022-01-26 analysis/Analysis ECDC forecasts.Rmd
split data files into smaller files
Former-commit-id: 78e173bad2cc7709054fe238f7f35717d59fbed1

```{r}
# load data 
# ------------------------------------------------------------------------------

hub_data <- rbindlist(list(
  fread(here("data", "full-data-european-forecast-hub-1.csv")), 
  fread(here("data", "full-data-european-forecast-hub-2.csv"))
)) |>
  unique()
```

>>>>

```{r}
# load data 
# ------------------------------------------------------------------------------
hub_data <- rbindlist(list(
  fread(here("data", "full-data-european-forecast-hub-1.csv")), 
  fread(here("data", "full-data-european-forecast-hub-2.csv")),
  fread(here("data", "full-data-european-forecast-hub-3.csv")),
)) |>
  unique()
```
